\documentclass{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{stmaryrd}
\usepackage{marvosym}
\usepackage{pifont}
\usepackage{fourier-orns}
\usepackage{hieroglf}
\geometry{a4paper, margin=1in}

\title{KubeFlash \\ \large Kubernetes Card Game}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Objective}
KubeFlash is a card game designed to help players learn and familiarize themselves with basic Kubernetes resources and functions.

\section*{Setup}
\begin{itemize}
    \item \textbf{Players:} 2-6
    \item \textbf{Deck:} 32 Kubernetes resource cards
    \item \textbf{Categories:} Workload, Network, Role Based Access Control (RBAC), Configuration, Storage, Event, Misc
    \item \textbf{Markers:} Namespaced {\LARGE$\boxdot$}, Global {\Mundus} or outside {\textpmhg{w}} resources
\end{itemize}

\section*{Rules}
At the beginning of the game the playing cards are shuffeled and placed face-down in a draw pile.
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Draw and Relay:} The player to the left of the active player (the one who will describe the resource) draws a card \textbf{without showing} it to anyone. They \textbf{only reveal the title} of the card to the player on their right (the active player).
    
    \item \textbf{Describe the Resource:} The active player must describe the resource from memory, covering:
    \begin{itemize}
        \item \textbf{Category} (Workload, Network, etc.)
        \item \textbf{Whether it is namespaced, global or outside}
        \item \textbf{Key function} or \textbf{usage} of the resource
    \end{itemize}
    The player does this \textbf{without seeing the card}, relying entirely on their knowledge.
    
    \item \textbf{Reveal and Score:} Once the active player has finished their description, the card is revealed to everyone (e.g. placed face-up on the table). The group determines if the active player describe the card correctly with regards to:
    \begin{itemize}
        \item \textbf{Category} (Workload, Network, etc.)
        \item \textbf{Whether it is namespaced, global or outside}
        \item \textbf{Key function} or \textbf{usage} of the resource
    \end{itemize}
	The card is given to the active player, if the active player described the card correctly. Otherwise the card is placed to a discard pile on the table.
    
    \item \textbf{Group Discussion:} After scoring, the group briefly discusses the resource to ensure everyone understands it.
\end{enumerate}
Once the draw pile is empty, each player counts the amount of cards scored. The players with the highest score win. There can be multiple winners if scores are tied.
\end{document}
